Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-06-01 doc/manuscript/manuscript.tex
Added to the manuscript

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{In current markets, the primary uses for soybean seed are in
products derived from it's oil or protein content. However, growers are
compensated based on seed oil so a more valuable crop is one with both
high yield, and high protein, oil, or a combination of the two. A
negative correlation between seed yield and seed protein makes improving
these traits simultaneously difficult but not impossible through
conventional breeding. A selection of lines with exceptional yield and
seed composition qualities was made from two recombinant inbred line
(RIL) soybean mapping populations to identify soybean varieties with
yield comparable to existing cultivars, and seed composition traits
superior to existing cultivars.}

@@

\hypertarget{version}{%
\section{Version}\label{version}}

This Rmd-skeleton uses the mdpi Latex template published 2019/02.
However, the official template gets more frequently updated than the
`rticles' package. Therefore, please make sure prior to paper
submission, that you're using the most recent .cls, .tex and .bst files
(available \href{http://www.mdpi.com/authors/latex}{here}).

@@

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL phenotype means to check means. Pearson correlation
coefficients between each phenotype were calculated and visualized with
the metan package.

@@

Materials and Methods should be described with sufficient details to
allow others to replicate and build on published results. Please note
that publication of your manuscript implicates that you must make all
materials, data, computer code, and protocols associated with the
publication available to readers. Please disclose at the submission
stage any restrictions on the availability of materials or information.
New methods and protocols should be described in detail while
well-established methods can be briefly described and appropriately
cited.

Research manuscripts reporting large datasets that are deposited in a
publicly available database should specify where the data have been
deposited and provide the relevant accession numbers. If the accession
numbers have not yet been obtained at the time of submission, please
state that they will be provided during review. They must be provided
prior to publication.

Interventionary studies involving animals or humans, and other studies
require ethical approval must list the authority that provided approval
and the corresponding ethical approval code.

@@

Several RILs in each of the tests had yield that was comparable to that
of their check cultivars. This was determined both quanititatively
through the use of contrasts between the mean of each RIL with the
average of the yield check means, and qualitatively by inspecting the
standard errors on the estimation of the genotype marginal means for
yield. No genotypes had yield that was quantitatively higher than that
of the yield checks, however many had comparable yield. Many of these
genotypes with comparable yield also had protein content that was
superior to the check average in each test. No genotypes had oil that
was superior to the check cultivars, but some had comparable yield and
oil content as well as superior protein content. These genotypes with
comparable yield and superior protein also had desirable agronomic
qualities such as low lodging and good seed quality which would make
them ideal candidates for future breeding material.

\hypertarget{genotypes-with-omparable-yield-and-oil-and-superior-protein}{%
\subsection{Genotypes with omparable yield and oil and superior
protein}\label{genotypes-with-omparable-yield-and-oil-and-superior-protein}}

@@

\caption{Soybean genotypes with yield and seed oil comparable to check cultivars, and seed protein superior to check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1635 & 65.32 (103\%) & 13 & 65.98 & 63.39 & 46.45 (103.1\%) & 4 & 42.92 & 45.05\\
\cmidrule{1-9}
N18-1783 & 67.38 (105.1\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1627 & 66.52 (103.7\%) & 10 &  &  & 46.01 (105.9\%) & 8 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1643 & 65.8 (102.6\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
\bottomrule
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

@@

\caption{Top 10 soybean genotypes on the basis of protein plus oil content.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein + Oil} & \multicolumn{4}{c}{Yield} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
Genotype & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1855 & 68.13 (107.5\%) & 2 &  &  & 43.17 (95.8\%) & 10 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1632-2 & 67.47 (106.4\%) & 3 &  &  & 46.34 (102.9\%) & 5 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1763 & 67.4 (106.3\%) & 5 &  &  & 39.45 (87.6\%) & 17 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1595 & 66.87 (105.5\%) & 6 &  &  & 43.52 (96.6\%) & 9 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1731 & 66.59 (105\%) & 7 &  &  & 43.16 (95.8\%) & 11 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1674 & 66.4 (104.7\%) & 8 & \multirow{-6}{*}{\raggedright\arraybackslash 65.98} & \multirow{-6}{*}{\raggedright\arraybackslash 63.39} & 44.26 (98.2\%) & 7 & \multirow{-6}{*}{\raggedright\arraybackslash 42.92} & \multirow{-6}{*}{\raggedright\arraybackslash 45.05}\\
\cmidrule{1-9}
N18-1575 & 69.04 (107.6\%) & 1 &  &  & 42.49 (97.8\%) & 12 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1761 & 68.48 (106.8\%) & 3 &  &  & 45.74 (105.3\%) & 9 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
N18-1769 & 67.95 (105.9\%) & 6 & \multirow{-3}{*}{\raggedright\arraybackslash 66.4} & \multirow{-3}{*}{\raggedright\arraybackslash 64.14} & 37.88 (87.2\%) & 18 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44}\\
\bottomrule
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{9}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

Subsection text here.

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=10 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/example_plot.pdf}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

@@

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
\begin{tabular}[t]{lrrrrrrrrrrr}
\toprule
\textbf{ } & \textbf{mpg} & \textbf{cyl} & \textbf{disp} & \textbf{hp} & \textbf{drat} & \textbf{wt} & \textbf{qsec} & \textbf{vs} & \textbf{am} & \textbf{gear} & \textbf{carb}\\
\midrule
Mazda RX4 & 21.0 & 6 & 160 & 110 & 3.90 & 2.620 & 16.46 & 0 & 1 & 4 & 4\\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 & 3.90 & 2.875 & 17.02 & 0 & 1 & 4 & 4\\
Datsun 710 & 22.8 & 4 & 108 & 93 & 3.85 & 2.320 & 18.61 & 1 & 1 & 4 & 1\\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 & 3.08 & 3.215 & 19.44 & 1 & 0 & 3 & 1\\
Hornet Sportabout & 18.7 & 8 & 360 & 175 & 3.15 & 3.440 & 17.02 & 0 & 0 & 3 & 2\\
\addlinespace
Valiant & 18.1 & 6 & 225 & 105 & 2.76 & 3.460 & 20.22 & 1 & 0 & 3 & 1\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:

\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}

The text continues here.

@@

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

@@

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

\hypertarget{patents}{%
\section{Patents}\label{patents}}

This section is not mandatory, but may be added if there are patents
resulting from the work reported in this manuscript.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{In current markets, the primary uses for soybean seed are in
products derived from it's oil or protein content. However, growers are
compensated based on seed oil so a more valuable crop is one with both
high yield, and high protein, oil, or a combination of the two. A
negative correlation between seed yield and seed protein makes improving
these traits simultaneously difficult but not impossible through
conventional breeding. A selection of lines with exceptional yield and
seed composition qualities was made from two recombinant inbred line
(RIL) soybean mapping populations to identify soybean varieties with
yield comparable to existing cultivars, and seed composition traits
superior to existing cultivars. The performance of these RILs were
evaluated in multiple environments and several genotypes were identified
with yield comparable to that of existing high-performance cultivars
with seed protein and or oil that is equal to or superior to the
high-performing cultivars. These genotypes will provide breeders with
additional sources of germplasm for continuing efforts to improve seed
composition traits, and provide growers with valuable genotype options.}

@@

@@

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL phenotype means to check means for all collected phenotypes.
Pearson correlation coefficients between each phenotype were calculated
with the metan package.

@@

@@

\hypertarget{phenotypic-correlations}{%
\subsection{Phenotypic correlations}\label{phenotypic-correlations}}

A strong negative correlation was observed in both tests between seed
protein and seed oil content. A coefficient of r = -0.93 was observed in
both populations. A negative correlation was observed between seed
protein and yield with correlation coefficient of r = -0.29 was observed
in both tests. This correlation was not statistically significant in
either population. A weak positive correlation was observed between seed
oil and seed yield in both populations. A correlation coefficient of r =
0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed
in Test 2. These correlation coefficients were not statistically
significant in either population.

\hypertarget{yield-contrasts}{%
\subsection{Yield contrasts}\label{yield-contrasts}}

Several RILs in each of the tests had yield that was comparable to that
of their check cultivars. This was determined both quanititatively
through the use of contrasts between the mean of each RIL with the
average of the yield check means, and qualitatively by inspecting the
standard errors on the estimation of the genotype marginal means for
yield. No genotypes had yield that was quantitatively higher than that
of the yield checks, however many had comparable yield. Many of these
genotypes with comparable yield also had protein content that was
superior to the check average in each test. No genotypes had oil that
was superior to the check cultivars, but some had comparable yield and
oil content as well as superior protein content.

RILs were also evaluated for lodging and seed quality. All RILs had seed
quality that was on par with that of the high-yielding checks however,
however 11 genotypes had lodging scores that were significantly greater
than the checks on the basis of contrasts. These RILs were removed from
consideration for recommendation on the basis of their relatively poor
agronomic performance.

\hypertarget{genotypes-with-comparable-yield-and-oil-and-superior-protein}{%
\subsection{Genotypes with comparable yield and oil and superior
protein}\label{genotypes-with-comparable-yield-and-oil-and-superior-protein}}

@@

\caption{Soybean genotypes with yield and seed oil comparable to check cultivars, and seed protein superior to check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10} \cmidrule(l{3pt}r{3pt}){11-14}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1635 & Jay Test 1 & 43.61 (106.5\%) & 16 & 45.09 & 40.94 & 46.45 (103.1\%) & 4 & 42.92 & 45.05 & 21.72 (96.7\%) & 3 & 20.89 & 22.45\\
\cmidrule{1-14}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  &  & 20.63 (96.5\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  &  & 20.62 (96.5\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1643 & \multirow{-3}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 45.7} & \multirow{-3}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44} & 21.45 (100.4\%) & 7 & \multirow{-3}{*}{\raggedright\arraybackslash 20.7} & \multirow{-3}{*}{\raggedright\arraybackslash 21.37}\\
\bottomrule
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

\hypertarget{genotypes-with-comparable-yield-and-superior-protein}{%
\subsection{Genotypes with comparable yield and superior
protein}\label{genotypes-with-comparable-yield-and-superior-protein}}

Seventeen out of the thirty RILs had a similar yield and superior
protein content to the check cultivars.

@@

\caption{Soybean RILs with superior protein content and comparable yield performance to high-yielding check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1763 &  & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1855 &  & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1595 &  & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1632-1 &  & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1620 &  & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1635 &  & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1731 &  & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1674 &  & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1682 &  & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1572 &  & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1751 & \multirow{-11}{*}{\raggedright\arraybackslash Jay Test 1} & 44.8 (109.4\%) & 12 & \multirow{-11}{*}{\raggedright\arraybackslash 45.09} & \multirow{-11}{*}{\raggedright\arraybackslash 40.94} & 41.59 (92.3\%) & 15 & \multirow{-11}{*}{\raggedright\arraybackslash 42.92} & \multirow{-11}{*}{\raggedright\arraybackslash 45.05}\\
\cmidrule{1-10}
N18-1761 &  & 49.1 (114.8\%) & 2 &  &  & 45.74 (105.3\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1575 &  & 48.67 (113.8\%) & 4 &  &  & 42.49 (97.8\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1769 &  & 48.58 (113.6\%) & 5 &  &  & 37.88 (87.2\%) & 18 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1643 & \multirow{-6}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-6}{*}{\raggedright\arraybackslash 45.7} & \multirow{-6}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-6}{*}{\raggedright\arraybackslash 43.65} & \multirow{-6}{*}{\raggedright\arraybackslash 43.44}\\
\bottomrule
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

@@

@@

@@

We have identified several genotypes with seed yield that is comparable
to existing cultivars that are commonly used in production. Many of
these genotypes have seed protein content that exceeds that of the check
cultivars, and some of these with superior protein have a seed oil
content that is comparable to these check cultivars as well. These
genotypes have good agronomic qualities as well and will provide both
breeders and growers with new options for genotypes that can be used in
production or used in breeding programs that seek to improve valuable
soybean seed composition traits.
